# R Project: Exploratory Data Analysis of Diamonds
---
title: "Data Visualization"
author: "patthapon nilkrom"
output: html_document
---
Explore data frame `diamonds` and create 5 visualizations.

```{r message=FALSE, warning=FALSE}
library(tidyverse)
head(diamonds)
```

### Relationship between carat and price
```{r message=FALSE, warning=FALSE}
set.seed(24)
ggplot(diamonds %>% sample_n(500),
       aes(carat, price)) +
  geom_point() + 
  geom_smooth() + 
  labs (
      title = "Relationship between carat and price", 
      caption = "Data source: Diamonds ggplot2")
```

-> we found a positive relationship between two variables.


### Bar chart of diamonds cut by color
```{r}
ggplot(diamonds, mapping = aes(cut, fill = color)) +
  geom_bar(position = "fill") + theme_minimal() + 
  labs (
      title = "Bar chart of diamonds cut by color", 
      caption = "Data source: Diamonds ggplot2")

```
-> we found chance of finding a grade J color diamond in any cut is very rare.


### Relationship between carat and price by color
```{r}
set.seed(24)
ggplot(diamonds %>% sample_n(1000),
       aes(carat, price, col=carat)) +
  geom_point() +
  geom_smooth(method = lm) + 
  theme_minimal() +
  facet_wrap(~color) +
  labs (
      title = "Relationship between carat and price by color", 
      caption = "Data source: Diamonds ggplot2")
```
-> we found carat weight affected the price of diamonds.

### Relationship between cut and price
```{r}
set.seed(24)
ggplot(diamonds %>% sample_n(1000), 
       aes(color, price, col=color)) +
  geom_boxplot() +
  theme_minimal() +
  labs (
      title = "Relationship between cut and price", 
      caption = "Data source: Diamonds ggplot2")
```
-> If we look at the color grading of diamonds and find that color grade J has the highest average price, it may be due to its rarity.

### Relationship of diamond price
```{r}
set.seed(24)
ggplot(diamonds %>% sample_n(1000),
       aes(carat, price, col=cut)) +
  geom_point() +
  theme_minimal()+
  scale_color_brewer(type = "qual", palette = 4) +
  labs (
      title = "Relationship of diamond price", 
      caption = "Data source: Diamonds ggplot2")
```
-> The higher the quality and carat weight of a diamonds, the higher its price tends to be.

